Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence and Forensic Workflow

### 2009-03-11 paper/paper.tex
More changes in the paper.

\begin{figure}
\fbox{
\begin{minipage}{.95\linewidth}
\begin{itemize}
\item The ability to store evidence from one or more physical
  devices.
\item Schema allowing evidence files to contain memory
  images, network packet intercepts, Netflow data, and extracted
  files.
\item Direct encoding of RAID configuration, allowing RAID volumes
  to be automatically reassembled from evidence files made of the
  physical RAID devices.
\item A revised compression system that allows individual chunks
  within a 16MB segment to be decompressed without decompressing the
  entire segment. 
\item Support for Global Distributed Evidence Management.
\end{itemize}
\end{minipage}}
\caption{Specific design goals for the next generation forensic file
  format.}
\end{figure}
\section{The Need for an Improved Forensic Format}

@@

\begin{itemize}
\item \emph{An Evidence Volume} is a single file with a \texttt{.aff}
  extension. 
\item \emph{An Evidence Set} is a collection of one or more Evidence
  Volumes. Evidence Sets can also be stored in object storage system (such as
  Amazon S3), or a hybrid---for example, metadata stored in an SQL
  database with physical data stored in large files in a file
  system. 
\item \emph{An Evidence Set UUID} is a unique identifier generated
  according to RFC4122\cite{rfc4122} for each new Evidence
  Set. Multiple Evidence Volumes that make up the same Evidence Set
  should all have the same UUID. When an Evidence Set is opened all its volumes are
  loaded, their UUIDs are checked, and all of their contents are
  logically merged so as to be visible as if they were all found in the same volume.
\item \emph{A segment} is a single unit of data written to volume. AFF4
  segments have a \emph{segment name}, a \emph{segment timestamp}, and
  a \emph{segment contents}.

\item \emph{A stream} is a collection of segments that can be
  concatenated together to form a single data object.

\item \emph{An image stream} is a stream that is dedicated to storing evidence from a single
  source of data.  For example, a stream may contain a disk image or a network
  capture. Whereas AFF could only support a single stream in an evidence
  file, AFF4 allows any number of streams to be stored. Each stream in
  the archive is  given a unique identifier.

\item \emph{A bevy} is a specific segment that is used to hold
  forensic image data, such as disk sectors, memory pages, or network
  packets. AFF1 used the term ``pages'' to describe bevys, but this
  term caused confusion when AFF was used to hold memory images, hence the
  new term.

\item \emph{A segment name} is the name under which a segment is
  stored within the archive. AFF4 segments have two-part names that
  typically contain a \emph{stream name} and \emph{bevy number}. For
  example the segment named \texttt{default/000001} refers to the stream
  called \texttt{default} and has a chunk name of \texttt{000001}. All segment
  names are encoded using UTF8. AFFLIB is being modified to allow any
  stream to be opened using the \texttt{af\_open} function; if a
  stream name is not specified, AFF4 implementations will open the
  stream named ``default.''

\item \emph{The segment timestamp} is a timestamp for the segment
  recorded in GMT.

\item \emph{Attributes} are a list of key/value pairs stored in each
stream's ``properties'' segment (e.g. ``stream/properties''). The
``properties'' file is a text file which stores attributes one on each
line. Attribute lines consist of the key, immediately followed by
``='' for text values or ``:'' for binary values. This is immediately
followed by the encoded value. Values containing text are encoded
using UTF8, while values containing binary data are encoded using
Base64. There may be multiple values for each attribute; in these
cases the order is preserved
by implementations. Implements may present different keys may be
presented in any order, however.
\vspace{1ex}
Each AFF4 archive must also have a top-level set of attributes---that
is, there is always a segment named ``properties.'' These volume
attributes are used to specify a Unique Identifier (UUID). (AFF1
stored each property in its own named segment. This created
significant overhead in many situations.)

\item \emph{A Target Reference} is a way of referencing objects. This is used
in a number of places which will be highlighted below. Using
references it is possible for the FIF file to refer to objects
embedded within itself, or within other FIF files. Its is also
possible to refer to external flat files. A number of usage scenarios
are described in Section \ref{usage_scenarios}. 
\end{itemize}

The Target Reference is an important AFF4 innovation: this mechanism
gives AFF4 files a way for describing evidence that is stored in
different evidence volumes, in the host computer's file system, or on
the Internet. We have defined the following target reference schema:

@@

\begin{itemize}
\item A reference in the format {\em aff://UUID/stream/segment} refers
to an external Evidence file set (identified by its UUID). If the segment
is missing (i.e. the reference ends with a ``/''), the reference is
for the entire stream. We do not specify a way of actually resolving
the UUID into a physical locations. This can achieved by
implementations using many methods, such as Active Directory, LDAP,
DNS, flat files or SQL databases.

\item A reference starting with {\em file://} refers to an external
file. The external file reference must be sanitised (to remove
.. directory traversal) and rooted at the current directory. A
filename of ``.'' refers to the current FIF volume.

\item A reference starting with {\em http://} refers to a HTTP
object which will be fetched. Support for this is optional.

\item A references ending with a ``/'' signifies a reference to a
stream in the current FIF file. The stream will be opened in its
entirety. If the reference does not end with a ``/'', the reference is
for a single segment.
\end{itemize}

>>>>

\begin{figure}
\fbox{
\begin{minipage}{.95\linewidth}
\begin{itemize}
\item The ability to store evidence from one or more physical
  devices.
\item Schema allowing evidence files to contain memory
  images, network packet intercepts, Netflow data, and extracted
  files.

%% Raid is only one example of the application of the map stream - the
%% most important might be the ability to use sleuthkit to generate
%% block allocation tables for all the files - thereby allowing
%% arbitrary programs to read individual files without using sleuthkit
\item Direct encoding of arbitrary mapping transformations of one or
more sources to allow multiple logical views. For example, allowing
RAID volumes to be automatically reassembled from evidence files made
of the physical RAID devices.
\item A revised compression system that allows individual chunks
  within a 16MB segment to be decompressed without decompressing the
  entire segment.
\item Support for Global Distributed Evidence Management.
\end{itemize}
\end{minipage}}
\caption{Specific design goals for the next generation forensic file
  format.}
\end{figure}
\section{The Need for an Improved Forensic Format}

@@

%% Since this is the itemised definition its probably better to
%% restrict it to the basic definitions and then move most of the
%% discussion a bit later. I want to show how concepts build on one
%% another - maybe even put a UML or class diagram

\begin{itemize}
\item \emph{An AFF Object} is the basic building block of our
file format. AFF Objects have a globally unique name (URN) as described in
\cite{RFC1737}. The name is defined within the aff2 namespace, and is
made unique by use of a unique identifier generated as per
RFC4122\cite{rfc4122}.

\item \emph{A Relation} is a statement about an AFF Object which
expresses some property of the object. The relation comprises of a
triple of (Subject, Attribute, Value). All metadata is reduced to the
triple notation.

\item \emph{An Evidence Volume} is a type of AFF Object which is
responsible for providing storage to AFF segments. Volumes may be
implemented in a number of ways, but must provide a mechanism for
storing and retrieving segments by their URN. We discuss several
Volume implementations below.

\item \emph{A segment} is a single unit of data written to a volume. AFF4
  segments have a \emph{segment name} provided by their URN, a
  \emph{segment timestamp} in GMT, and the \emph{segment contents}.

\item \emph{A stream} is an AFF Object which provides the ability to
seek and read random data. Stream objects are free to implement their storage
in a number of ways, but must provide clients the stream like
interface. We discuss a number of stream types below.

% Is it important to define this? do we use it?
%\item \emph{An Evidence Set} is a loose collection of one or more Evidence
%Volumes.

%Evidence Sets can also be stored in object storage system (such as
%  Amazon S3), or a hybrid---for example, metadata stored in an SQL
%  database with physical data stored in large files in a file
%  system.

% I would describe this process after the definitions.

%\item \emph{An Evidence Set UUID} is a unique identifier generated
%  according to RFC4122\cite{rfc4122} for each new Evidence
%  Set. Multiple Evidence Volumes that make up the same Evidence Set
%  should all have the same UUID. When an Evidence Set is opened all its volumes are
%  loaded, their UUIDs are checked, and all of their contents are
%  logically merged so as to be visible as if they were all found in
% the same volume.

%% I Wonder if this explaination should be postposed to the section we
%% actually discuss it - otherwise we duplicate it again
%% \item \emph{An image stream} is a stream that is dedicated to storing evidence from a single
%%  source of data.  For example, a stream may contain a disk image or a network
%%  capture. Whereas AFF could only support a single stream in an evidence
%%  file, AFF4 allows any number of streams to be stored. Each stream in
%%  the archive is  given a unique identifier.

%%\item \emph{A bevy} is a specific segment that is used to hold
%%  forensic image data, such as disk sectors, memory pages, or network
%%  packets. AFF1 used the term ``pages'' to describe bevys, but this
%%  term caused confusion when AFF was used to hold memory images, hence the
%%  new term.

%% This is no longer correct - segment names are URNs and are encoded
%% according to RFC1737 as mentioned above.
%%\item \emph{A segment name} is the name under which a segment is
%%  stored within the archive. AFF4 segments have two-part names that
%%  typically contain a \emph{stream name} and \emph{bevy number}. For
%%  example the segment named \texttt{default/000001} refers to the stream
%%  called \texttt{default} and has a chunk name of \texttt{000001}. All segment
%%  names are encoded using UTF8. AFFLIB is being modified to allow any
%%  stream to be opened using the \texttt{af\_open} function; if a
%%  stream name is not specified, AFF4 implementations will open the
%%  stream named ``default.''

%%\item \emph{The segment timestamp} is a timestamp for the segment
%%  recorded in GMT.

%% This should be discussed as a way we are storing the RDF triples,
%% rather than as a definition.
%% \item \emph{Attributes} are a list of key/value pairs stored in each
%% stream's ``properties'' segment (e.g. ``stream/properties''). The
%% ``properties'' file is a text file which stores attributes one on each
%%line. Attribute lines consist of the key, immediately followed by
%%``='' for text values or ``:'' for binary values. This is immediately
%%followed by the encoded value. Values containing text are encoded
%%using UTF8, while values containing binary data are encoded using
%%Base64. There may be multiple values for each attribute; in these
%%cases the order is preserved
%%by implementations. Implements may present different keys may be
%%presented in any order, however.
%%\vspace{1ex}

%% This is not correct any more as volumes must store their own URN in
%% a different way (the zip implementation uses an archive comment for
%% this).

%% Each AFF4 archive must also have a top-level set of attributes---that
%% is, there is always a segment named ``properties.'' These volume
%% attributes are used to specify a Unique Identifier (UUID). (AFF1
%% stored each property in its own named segment. This created
%% significant overhead in many situations.)

%% Since target references are all just URNs now the resolving is automatic.

\item \emph{A Target Reference} is a way of referencing objects by use
of a Uniform Resource Identifier (URI). The URI can be another AFF
Object URN or may be a more general Uniform Resource Locator (URL),
such as for example a HTTP or FTP object.

\item \emph{The Resolver} is a central data store which collects and resolves
attributes for the different AFF Objects. We discuss the Resolver in
detail in Section \ref{resolver}.

%%in a number of places which will be highlighted below. Using
%%references it is possible for the FIF file to refer to objects
%%embedded within itself, or within other FIF files. Its is also
%%possible to refer to external flat files. A number of usage scenarios
%%are described in Section \ref{usage_scenarios}. 
\end{itemize}

Since AFF Objects have globally unique URNs it is possible for an
Object in one volume to refer to an object in another volume. The
resolver has visibility of all URNs and their current physical
location.

%The Target Reference is an important AFF4 innovation: this mechanism
%gives AFF4 files a way for describing evidence that is stored in
%different evidence volumes, in the host computer's file system, or on
%the Internet. We have defined the following target reference schema:

@@

%\begin{itemize}
%\item A reference in the format {\em aff://UUID/stream/segment} refers
%to an external Evidence file set (identified by its UUID). If the segment
%is missing (i.e. the reference ends with a ``/''), the reference is
%for the entire stream. We do not specify a way of actually resolving
%the UUID into a physical locations. This can achieved by
%implementations using many methods, such as Active Directory, LDAP,
%DNS, flat files or SQL databases.

%\item A reference starting with {\em file://} refers to an external
%file. The external file reference must be sanitised (to remove
%.. directory traversal) and rooted at the current directory. A
%filename of ``.'' refers to the current FIF volume.

%\item A reference starting with {\em http://} refers to a HTTP
%object which will be fetched. Support for this is optional.

%% This is no longer correct as all segments, streams and volumes have
%% a unique URN so we dont need to make these distinctions.

%% \item A references ending with a ``/'' signifies a reference to a
%% stream in the current FIF file. The stream will be opened in its
%% entirety. If the reference does not end with a ``/'', the reference is
%% for a single segment.
%%\end{itemize}
